### 2021-07-10 docs/manuscript/manuscript.tex
Rephrase sigmoid section

The input function is a sigmoid function described by Eq~\ref{ec:input-func}.
\begin{equation}
 g(u^i) = \frac{1}{1 + \exp(a - b \cdot u^i)},
 \label{ec:input-func}
\end{equation}
\noindent
in which $a$ is the sigmoid steepness, equal to 5; $a/b$ is the threshold value,
set to 1 for all simulations, and $u^i$ is the following equation:
\begin{equation}
 u^i = \sum_j w_{ij} \cdot [G]^j_n + w_{im} \cdot [M]_n.
 \label{ec:mat-sum}
\end{equation}

@@

In order to group all the isomorphic (i.e. topologically equivalent) networks from
the totality (2061) of sampled GRNs we used a
classification algorithm that selected a random GRN, then it generated all
isomorphs of that GRN by performing permutations in rows and columns. The
algorithm then compared all six isomorphs with other GRN and classified the
topologies in the same group if they were isomorphic networks.

>>>>

Sigmoid functions are often used to approximate Hill functions describing gene
activation/inhibition in which steepness can be modulated by mechanisms as
molecular cooperativity and target sequestration \cite{ricci2011}. This approach
has been used extensively to model the response of signaling pathways and gene
interactions in GRNs \cite{mendoza2006, vu2007, zhang2013, armao2016}.
Moreover, differential equation models using sigmoid functions have shown to
fit gene expression data \cite{chen2005, dahlquist2015}. In this study, the
input function representing regulatory interactions is a sigmoid function
described by Eq~\ref{ec:input-func}.

\begin{equation}
 g(u^i) = \frac{1}{1 + \exp(a - b \cdot u^i)},
 \label{ec:input-func}
\end{equation}
\noindent
in which $a$ is the sigmoid steepness, equal to 5; $a/b$ is the threshold value,
set to 1 for all simulations, and $u^i$ is the following equation:
\begin{equation}
 u^i = \sum_j w_{ij} \cdot [G]^j_n + w_{im} \cdot [M]_n.
 \label{ec:mat-sum}
\end{equation}

@@

In order to group all the isomorphic (i.e. topologically equivalent) networks from
the totality (2061) of sampled GRNs we used a
classification algorithm that selected a random GRN and generated all
isomorphs of that GRN by interchanging rows of the adjacency matrix
($i \leftrightarrow j$) while interchanging the corresponding columns
($i+1 \leftrightarrow j+1$). The
algorithm then compared all six isomorphs with other GRN and classified the
topologies in the same group if they were isomorphic networks.
